Lasso_RCI_Response

### 2024-06-28 Lasso_RCI_Response.Rmd
don't need dis stuff

# Libraries
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library(fuzzySim) ## For FDR adjusted p values
library(broom) # for tidy regression output
```

@@

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
```

```{r}

AAQIIpre <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
AAQIIpre <- AAQIIpre |>
  mutate(
    AAQIIpre = AAQIIpre_1_1 + AAQIIpre_2_1 + AAQIIpre_3_1 + AAQIIpre_4_1 + 
      AAQIIpre_5_1 + AAQIIpre_6_1 + AAQIIpre_7_1
  )
Mothership <- left_join(Mothership,AAQIIpre, by = join_by(ID1 == ID1))

AAQIIpost <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPost_1.sav")
AAQIIpost <- AAQIIpost |>
  mutate(
    AAQIIpost = AAQIIpost_1_1 + AAQIIpost_2_1 + AAQIIpost_3_1 + AAQIIpost_4_1 + 
      AAQIIpost_5_1 + AAQIIpost_6_1 + AAQIIpost_7_1
  )
Mothership <- left_join(Mothership,AAQIIpost, by = join_by(ID1 == ID1))

FMMQ_pre <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPre_1.sav")
FMMQ_pre <- FMMQ_pre|>
  mutate(
    #reverse code items
    FFMQpre_4R  = 6 - FFMQpre_4_1,
    FFMQpre_5R  = 6 - FFMQpre_5_1,  
    FFMQpre_7R  = 6 - FFMQpre_7_1, 
    FFMQpre_8R  = 6 - FFMQpre_8_1, 
    FFMQpre_11R = 6 - FFMQpre_11_1, 
    FFMQpre_12R = 6 - FFMQpre_12_1,
    FFMQpre_14R = 6 - FFMQpre_14_1,
    FFMQpre_17R = 6 - FFMQpre_17_1,
    FFMQpre_19R = 6 - FFMQpre_19_1,
    FFMQpre_22R = 6 - FFMQpre_22_1,
    FFMQpre_23R = 6 - FFMQpre_23_1,
    FFMQpre_24R = 6 - FFMQpre_24_1,
    #create scales
    Desc_Ex_pre =
        FFMQpre_1_1 + FFMQpre_2_1 + FFMQpre_5R + FFMQpre_11R + FFMQpre_16_1,
    Non_react_pre = 
        FFMQpre_3_1 + FFMQpre_9_1 + FFMQpre_13_1 + FFMQpre_18_1 + FFMQpre_21_1,
    Observe_inner_pre = 
        FFMQpre_6_1 + FFMQpre_10_1 + FFMQpre_15_1 + FFMQpre_20_1,
    Self_compasion_pre = 
        FFMQpre_4R + FFMQpre_7R + FFMQpre_14R + FFMQpre_19R + FFMQpre_24R,
    Acting_mindful_pre = 
        FFMQpre_8R + FFMQpre_12R + FFMQpre_17R + FFMQpre_22R + FFMQpre_23R,
    FFMQ_pre_total = 
        Desc_Ex_pre + Non_react_pre + Observe_inner_pre+ Self_compasion_pre + Acting_mindful_pre
    )
Mothership <- left_join(Mothership,FMMQ_pre, by = join_by(ID1 == ID1))

FMMQ_post <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_1.sav")
FMMQ_post <- FMMQ_post|>
  mutate(
    #reverse code items
    FFMQpost_4R  = 6 - FFMQpost_4_1,
    FFMQpost_5R  = 6 - FFMQpost_5_1,  
    FFMQpost_7R  = 6 - FFMQpost_7_1, 
    FFMQpost_8R  = 6 - FFMQpost_8_1, 
    FFMQpost_11R = 6 - FFMQpost_11_1, 
    FFMQpost_12R = 6 - FFMQpost_12_1,
    FFMQpost_14R = 6 - FFMQpost_14_1,
    FFMQpost_17R = 6 - FFMQpost_17_1,
    FFMQpost_19R = 6 - FFMQpost_19_1,
    FFMQpost_22R = 6 - FFMQpost_22_1,
    FFMQpost_23R = 6 - FFMQpost_23_1,
    FFMQpost_24R = 6 - FFMQpost_24_1,
    #create scales
    Desc_Ex_post =
        FFMQpost_1_1 + FFMQpost_2_1 + FFMQpost_5R + FFMQpost_11R + FFMQpost_16_1,
    Non_react_post = 
        FFMQpost_3_1 + FFMQpost_9_1 + FFMQpost_13_1 + FFMQpost_18_1 + FFMQpost_21_1,
    Observe_inner_post = 
        FFMQpost_6_1 + FFMQpost_10_1 + FFMQpost_15_1 + FFMQpost_20_1,
    Self_compasion_post = 
        FFMQpost_4R + FFMQpost_7R + FFMQpost_14R + FFMQpost_19R + FFMQpost_24R,
    Acting_mindful_post = 
        FFMQpost_8R + FFMQpost_12R + FFMQpost_17R + FFMQpost_22R + FFMQpost_23R,
    FFMQ_post_total = 
        Desc_Ex_post + Non_react_post + Observe_inner_post + Self_compasion_post + Acting_mindful_post
    )
Mothership <- left_join(Mothership,FMMQ_post, by = join_by(ID1 == ID1))

# df_5 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_4250-4350.sav")
```

@@

# only include people that attend treatment & its thier first time attending
Mothership <- Mothership |>
  filter(
    is.na(Prev_AdmitID_1),
    C_Admit_1 == 1
  ) |>
  mutate(
    dummy = -99
  )
  # filter(!is.na(Disorder_treat),
  #        !is.na(TxYear),
  #        !is.na(Duration))

@@

@@

library(JTRCI)

# # 
# # #devtools::install_github("zieglema/ClinicalSig")
# #1. Create df for RCI
# RCI_df_dep <- Mothership_post |>
#   mutate(
#     ID1  = as.integer(ID1),
#     pre  = as.numeric(CUDOS_pre),
#     post = as.numeric(CUDOS_post),
#   ) |>
#   select(
#     ID1,pre,post
#   ) |>
#   filter(!is.na(pre),
#          !is.na(post),
#          pre > 20)
# 
# RCI_df_anx <- Mothership_post |>
#   mutate(
#     ID1  = as.integer(ID1),
#     pre  = as.numeric(CUXOS_pre),
#     post = as.numeric(CUXOS_post),
#   ) |>
#   select(
#     ID1,pre,post
#   ) |>
#   filter(!is.na(pre),
#          !is.na(post),
#          pre > 20)
# 
# 
# RCI_df_dep <- data.frame(RCI_df_dep)
# RCI_df_anx <- data.frame(RCI_df_anx)
# 
# # https://awkruijt.netlify.app/plotposts/longitudinaljtrci
# 
# RCI_df_anx1<-RCI_df_anx |>
#   select(ID1,pre,post)
# 
# ## Using RCI only (respond/nonrespond/deteriorated)
# DEP_RCI <- JTRCI (data = RCI_df_dep, 
#                   pre = "pre", 
#                   post = "post", 
#                   ppid = "ID1", 
#                   reliability = .74, 
#                   indextype = "RCI", 
#                   JTcrit = "auto",
#                   plottitle = "JT indices for anxiety")
# 
# ANX_RCI <- JTRCI (data = RCI_df_anx, 
#                   pre = "pre", 
#                   post = "post", 
#                   ppid = "ID1", 
#                   reliability = .74, 
#                   indextype = "RCI", 
#                   #JTcrit = "auto",
#                   plottitle = "JT indices for depression")
# RCI_DF<- ANX_RCI$data
# colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")
# 
# RCI_DF2<- DEP_RCI$data
# colnames(RCI_DF2) <- paste0(colnames(RCI_DF2),"_dep")
# 
# RCI_DF <- full_join(RCI_DF,RCI_DF2, by = c("ppid_anx" = "ppid_dep"))
# colnames(RCI_DF)[1] = "ID1"
# 
# head(RCI_DF)
```

```{r}
#Using JT citeria (recovered/improved/nonresponse/deteriorated)
# 
# #1. JT classification for depression
# JTRCI (data = RCI_df_dep, 
#                   pre = "pre", 
#                   post = "post", 
#                   ppid = "ID1", 
#                   reliability = .74, 
#                   indextype = "JT", 
#                   JTcrit = "auto",
#                   plottitle = "JT indices for anxiety")
# 
# DEP_JT <- JTRCIdf
# colnames(DEP_JT) <- paste0(colnames(DEP_JT),"_dep")
# head(DEP_JT)
# 
# #2. JT classification for anxiety
# JTRCI (data = RCI_df_anx, 
#                   pre = "pre", 
#                   post = "post", 
#                   ppid = "ID1", 
#                   reliability = .74, 
#                   indextype = "JT", 
#                   #JTcrit = "auto",
#                   plottitle = "JT indices for depression")
# 
# ANX_JT<- JTRCIdf
# 
# #3. Make combined JT table for anxiety and depression
# 
# # JT_DF<- ANX_JT
# 
# colnames(ANX_JT) <- paste0(colnames(ANX_JT),"_anx")
# 
# # 
# # JT_DF2<- DEP_JT
# 
# # 
# # JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
# # colnames(JT_DF)[1] = "ID1"
# 
# head(ANX_JT)
```

JTRCI with less people
```{r}

Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    # rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
    #ACT stuff
    # AAQIIpre, AAQIIpost,
    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
    # Acting_mindful_pre,
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post,
  ))

Mothership_lasso_1 <- na.omit(Mothership_lasso)

dim(Mothership_lasso_1)

@@

```{r}
RCI_df_anx2 <- Mothership_lasso_1 |>
  filter(
    !is.na(CUXOS_pre),
    !is.na(CUXOS_post),
    CUXOS_pre > 20,
  )|>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

RCI_df_dep2 <- Mothership_lasso_1 |>
  filter(
    !is.na(CUDOS_pre),
    !is.na(CUDOS_post),
    CUDOS_pre > 20,
  ) |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

RCI_df_dep2 <- data.frame(RCI_df_dep2)
RCI_df_anx2 <- data.frame(RCI_df_anx2)

#1. JT classification for depression
JTRCI (data = RCI_df_dep2, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "JT", 
                  JTcrit = "auto",
                  plottitle = "JT indices for Depression")

DEP_JT_smol <- JTRCIdf
colnames(DEP_JT_smol) <- paste0(colnames(DEP_JT_smol),"_dep")
head(DEP_JT_smol)

#2. JT classification for anxiety
JTRCI (data = RCI_df_anx2, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "JT", 
                  #JTcrit = "auto",
                  plottitle = "JT Indices For Anxiety")

ANX_JT_smol<- JTRCIdf

colnames(ANX_JT_smol) <- paste0(colnames(ANX_JT_smol),"_anx")
```

@@

# Mothership_post <- Mothership_post |>
#   #1. Filter out scores for people not in the program / don't have data
#   filter(!is.na(Days_complete_1)) |>
#   #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
#   filter(!is.na(CUXOS_pre),
#          !is.na(CUXOS_post),
#          CUXOS_pre > 0,
#          CUXOS_post >= 0,
#          !is.na(CUDOS_pre),
#          !is.na(CUDOS_post),
#          CUDOS_pre > 0,
#          CUDOS_post>= 0
#          ) |>
#   mutate(
#     Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
#     Delta_Dep_DC = CUDOS_post - CUDOS_pre,
#     Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
#     Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100
#   )
```

```{r}
#Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    # Anx_Responder = as.factor(
    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  <= -50, "Responder",
    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
    #   )),
    # Dep_Responder = as.factor(
    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange <= -50, "Responder",
    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
    #   )),
    # Treatment_Responder = as.factor(
    #   ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
    #   ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      # )))))))))))

#2. Left join data from the RCI dataset into the Mothership_post df
# Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
#   mutate(
#     Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
#     Depression_Responder = as.factor(recode(Depression_Responder,
#                                             "1" = "2",
#                                             "2" = "2",
#                                             "3" = "1"
#     )),
#     Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
#     Depression_Responder = as.factor(recode(Depression_Responder,
#                                             "2" = "Non-Responder",
#                                             "1" = "Responder"
#     )),
#     Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
#                                          "1" = "2",
#                                          "2" = "2",
#                                          "3" = "1"
#     )),
#     Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
#                                          "2" = "Non-Responder",
#                                          "1" = "Responder"
#     )),
#     RESPONDER_FIGS = as.factor(
#       ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
#              ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
#       ))) |>
#   filter(!is.na(RESPONDER_FIGS))
```

JT Numbers
```{r}
Mothership_post_anx <- left_join(Mothership_post,ANX_JT_smol, by = join_by(ID1 == ppid_anx)) |>
  mutate(
    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "1" = "2",
                                         "2" = "2",
                                         "3" = "1",
                                         "4" = "1",
                                         "5" = "1"
    )),
    # Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, NA)),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "2" = "Non-Responder",
                                         "1" = "Responder"
    ))) |>
  filter(
    !is.na(Anxiety_Responder),
    )

Mothership_post_dep <- left_join(Mothership_post,DEP_JT_smol, by = join_by(ID1 == ppid_dep)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "1" = "2",
                                            "2" = "2",
                                            "3" = "1",
                                            "4" = "1",
                                            "5" = "1"
    )),
    # Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, NA)),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "2" = "Non-Responder",
                                            "1" = "Responder"
    ))) |>
  filter(
    !is.na(Depression_Responder)
    )

Mothership_post_joined <- full_join(Mothership_post_dep,Mothership_post_anx, by = join_by(ID1 == ID1), suffix = c(".x",".y")) |>
  select(-ends_with(".y"))

#It saves everything colname.x, so I'm going to remove the .x from everything
names.x <- colnames(Mothership_post_joined)[2:248]
colnames(Mothership_post_joined)[2:248] <- substr(names.x,1,nchar(names.x)-2)
```

RCI numbers
```{r}
# Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
#   mutate(
#     Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
#     Depression_Responder = as.factor(recode(Depression_Responder,
#                                             "1" = "2",
#                                             "2" = "2",
#                                             "3" = "1",
#                                             "4" = "1",
#                                             "5" = "1"
#     )),
#     Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
#     Depression_Responder = as.factor(recode(Depression_Responder,
#                                             "2" = "Non-Responder",
#                                             "1" = "Responder"
#     )),
#     Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
#                                          "1" = "2",
#                                          "2" = "2",
#                                          "3" = "1",
#                                          "4" = "1",
#                                          "5" = "1"
#     )),
#     Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
#                                          "2" = "Non-Responder",
#                                          "1" = "Responder"
#     ))) |>
#   filter(
#     !is.na(Anxiety_Responder),
#     !is.na(Depression_Responder)
#     )
```

# Data analysis 
## Part 1: Methods information
```{r}
# summary(as.factor(Mothership_post_joined$SCID_1))
```

## Part 2: Who is attending?

### Demographics information
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of pre-post change???
- Table 4: demographic breakdown

>>>>

# Libraries
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
```

@@

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")

@@

# only include people that attend treatment & its thier first time attending
Mothership <- Mothership |>
  filter(
    is.na(Prev_AdmitID_1),
    C_Admit_1 == 1
  ) |>
  mutate(
    dummy = -99
  ) |>
  filter(!is.na(Disorder_treat),
         !is.na(TxYear),
         !is.na(Duration))

@@

```{r}
Mothership_lasso_1 <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    CUXOS_pre >= 20,
    CUDOS_pre >= 20
  ) |>
  select( c(
   # Anxiety_Responder, Depression_Responder,
    # Demographics
    ID1, Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, 
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post
  ))

Mothership_lasso_1 <- na.omit(Mothership_lasso_1)
```

@@

library(JTRCI)
citation("JTRCI")

# 
# #devtools::install_github("zieglema/ClinicalSig")
#1. Create df for RCI
RCI_df_dep <- Mothership_lasso_1 |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20,
         !is.na(Some_College),
         !is.na(Female),
         !is.na(IPT_track_1),
         !is.na(White),
         CUXOS_pre >= 20,
         CUDOS_pre >= 20) |>
  select(
    ID1,pre,post)

RCI_df_anx <- Mothership_lasso_1 |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post)
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20,
         !is.na(Some_College),
         !is.na(Female),
         !is.na(IPT_track_1),
         !is.na(White),
         CUXOS_pre >= 20,
         CUDOS_pre >= 20
  ) |>
  select(
    ID1,pre,post
  )

RCI_df_dep <- data.frame(RCI_df_dep)
RCI_df_anx <- data.frame(RCI_df_anx)

# https://awkruijt.netlify.app/plotposts/longitudinaljtrci

RCI_df_anx1<-RCI_df_anx |>
  select(ID1,pre,post)

## Using RCI only (respond/nonrespond/deteriorated)
DEP_RCI <- JTRCI (data = RCI_df_dep, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  JTcrit = "auto",
                  plottitle = "JT indices for anxiety")

ANX_RCI <- JTRCI (data = RCI_df_anx, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  #JTcrit = "auto",
                  plottitle = "JT indices for depression")
RCI_DF<- ANX_RCI$data
colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")

RCI_DF2<- DEP_RCI$data
colnames(RCI_DF2) <- paste0(colnames(RCI_DF2),"_dep")

RCI_DF <- full_join(RCI_DF,RCI_DF2, by = c("ppid_anx" = "ppid_dep"))
colnames(RCI_DF)[1] = "ID1"

RCI_DF
```

```{r}
#Using JT citeria (recovered/improved/nonresponse/deteriorated)

#1. JT classification for depression
JTRCI (data = RCI_df_dep, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "JT") 
                  #plottitle = "JT indices for anxiety")

DEP_JT <- JTRCIdf

#2. JT classification for anxiety
JTRCI (data = RCI_df_anx, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "JT") 
                  #JTcrit = "auto",
                 # plottitle = "JT indices for depression")

ANX_JT<- JTRCIdf

#3. Make combined JT table for anxiety and depression

JT_DF<- ANX_JT

colnames(JT_DF) <- paste0(colnames(JT_DF),"_anx")

JT_DF2<- DEP_JT
colnames(JT_DF2) <- paste0(colnames(JT_DF2),"_dep")

JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
colnames(JT_DF)[1] = "ID1"

JT_DF

@@

@@

Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have data
  filter(!is.na(Days_complete_1)) |>
  #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) 
  # mutate(
  #   Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
  #   Delta_Dep_DC = CUDOS_post - CUDOS_pre,
  #   Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
  #   Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
  #   #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
  #   Anx_Responder = as.factor(
  #     ifelse(CUXOS_pre <= 20 & Percent_Anx_change  <= -50, "Responder",
  #     ifelse(CUXOS_pre <= 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
  #     )),
  #   Dep_Responder = as.factor(
  #     ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange <= -50, "Responder",
  #     ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
  #     )),
  #   Treatment_Responder = as.factor(
  #     ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
  #     ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
  #     ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
  #     ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
  #     ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
  #     ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
  #     ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
  #     ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
  #     ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
  #     )))))))))))

Mothership_post <- left_join(Mothership_post,JT_DF, by = join_by(ID1 == ID1)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "1" = "2",
                                            "2" = "2",
                                            "3" = "1",
                                            "4" = "1",
                                            "5" = "1"
    )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "2" = "Non-Responder",
                                            "1" = "Responder"
    )),
    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "1" = "2",
                                         "2" = "2",
                                         "3" = "1",
                                         "4" = "1",
                                         "5" = "1"
    )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "2" = "Non-Responder",
                                         "1" = "Responder"
    ))) |>
  filter(
    !is.na(Anxiety_Responder),
    !is.na(Depression_Responder)
    )
```

```{r}
#############            AnxDep_PrePost                 ##################

#7. create new DF with Varaibles we want

AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                   Mothership_post$Disorder_treat,
                                   Mothership_post$BL_CUDOS,
                                   Mothership_post$BL_CUXOS,
                                   Mothership_post$CUDOS_pre,
                                   Mothership_post$CUDOS_post,
                                   Mothership_post$CUXOS_pre,
                                   Mothership_post$CUXOS_post,
                                   #Extra stuff?
                                   Mothership_post$Depression_Responder,
                                   Mothership_post$Anxiety_Responder
                                   #Mothership_post$RESPONDER_FIGS
)) #%>%
#filter(!is.na(Mothership_post$Disorder_treat))

colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "BL_CUDOS", "BL_CUXOS", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","Depression_Responder",
                             "Anxiety_Responder")
#, "RESPONDER_FIGS")

#8. Create long data frame

AnxDep_PrePost_Long <- AnxDep_PrePost %>% 
  pivot_longer(
    cols = CUDOS_pre:CUXOS_post, 
    names_to = "Test",
    values_to = "Score"
  )
AnxDep_PrePost_Long <-AnxDep_PrePost_Long %>%
  mutate(
    PrePost = ifelse(
      Test == "CUDOS_pre", "Pre",
      ifelse(Test == "CUXOS_pre" , "Pre", "Post"
      )),
    Score = as.integer(Score),
    Test = as.factor(Test),
    Test = as.factor(ifelse(Test == "CUDOS_pre",  "CUDOS",
                            ifelse(Test == "CUDOS_post", "CUDOS", "CUXOS"
                            ))))

#9. Convert to data frame with means of values to be plotted
AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
  group_by(Test,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))
```

# Data analysis 
## Part 1: Who is attending?

### Demographics information
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of pre-post change???
- Table 4: demographic breakdown
```{r}
Mothership_lasso <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Anxiety_Responder),
    !is.na(Depression_Responder),
    CUXOS_pre >= 20,
    CUDOS_pre >= 20
  ) |>
  select( c(
    Anxiety_Responder, Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, 
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
  ))

Mothership_lasso <- na.omit(Mothership_lasso)

summary(Mothership_lasso$Anxiety_Responder)
